---
title: "Our recent (post-2017) publications..."
linestretch: 1.5
blinded: true
colorlinks: true
numbersections: true
---

```{r Setup, include=FALSE, results="hide", warning=FALSE}
require(knitr)
require(pander)
require(memisc)
require(Cairo)
require(ggplot2)
require(extrafont)
loadfonts()
panderOptions('knitr.auto.asis', FALSE)

opts_chunk$set(dev=c("png","pdf"),
               fig.lp="fig:",
               cache=FALSE,
               par=TRUE,
               echo=FALSE,
               results="hide", ## not 'markup' or 'asis'
               message=FALSE,
               warning=FALSE,
               dpi=300)
addNotes <- function(tab, cap) {
    tab <- gsub("\\^\\{(\\*+)\\}", "\\\\\\text{\\1}", tab)
    paste0("\\begin{table} \\centering",
           tab,
           "\\\\ \\sffamily \\emph{Notes:} ",
           "* = p < 0.05; ** = p < 0.01; *** = p < 0.001",
           "\\caption{",
           cap,
           "}",
           "\\end{table}")
}

```

```{r data}
pretty_names <- c("Nick Allen",
                  "Michael Bacon",
                  "Giacomo Benedetto",
                  "Michelle Bentley",
                  "Licia Cianetti",
                  "Tom Dyson",
                  "Neil Gascoigne",
                  "Andreas Goldthau",
                  "Ursula Hackett",
                  "Sandra Halperin",
                  "Chris Hanretty",
                  "Oliver Heath",
                  "Will Jones",
                  "Ben O'Loughlin",
                  "Ivica Petrikova",
                  "Rebecca Roache",
                  "Jonathan Seglow",
                  "John Sellars",
                  "James Sloam",
                  "Kaat Smets",
                  "Henry Somers-Hall",
                  "Thomas Stubbs",
                  "Dan Whistler",
                  "Nathan Widder",
                  "Jinghan Zeng")

urls <- c("https://pure.royalholloway.ac.uk/portal/en/persons/nicholas-allen(f69c6bc8-318f-4578-961a-9a7d3cf07b21)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/michael-bacon(c6cd3424-0472-4985-ab96-4cce588eef01)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/giacomo-benedetto(7d67c091-a49e-4942-a656-a4b431769845)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/michelle-bentley(7cf349f5-bb36-46e8-8810-fa792348242c)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/licia-cianetti(eb93895b-be21-4932-88c4-5b8a727ead95)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/tom-dyson(ad8e5533-fbc1-43b0-984a-d66d54900ded)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/neil-gascoigne(39e64736-de38-4e69-b007-8db2bdfaf014)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/andreas-goldthau(fa61069f-7b3d-4689-b125-54cbb37c8ac4)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/ursula-hackett(36bc1d93-6ed9-423b-aeee-844ee6f2e5c6)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/sandra-halperin(a3edddc2-9123-4c9c-9a98-83bfb0f466e6)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/christopher-hanretty(69469d99-0aa0-4f63-87a9-b96dbd86373d)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/oliver-heath(5ae90ce4-2542-4f98-9168-2762f43d5ebc)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/william-jones(c6c4e700-3e39-4b36-bad0-860f5b1c4a7b)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/ben-oloughlin(1273572d-2dc3-4680-bd44-f007a312b007)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/ivica-petrikova(5002a317-3946-4dd6-8657-3f5f5088a7e7)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/rebecca-roache(59a8d9fa-c44f-4e78-9626-a78500c9013d)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/jonathan-seglow(6ccf091b-8111-4388-84b1-ebc6777f8a1b)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/john-sellars(709b3ed0-efe1-45cc-923f-9d180a42fb9a)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/james-sloam(bdd4ef87-7beb-4fc1-8a81-a2c9119a137e)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/kaat-smets(e1374f99-c608-4884-9554-10ec82dfbf69)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/henry-somershall(9b215915-fcd6-4567-8463-c0c39f5aed70)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/thomas-stubbs(bfb60e1a-01c8-40d5-9fd1-7d05810abf78)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/daniel-whistler(72b7b1f7-5dff-418e-a807-2b1c2e50ca31)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/nathan-widder(2dbed1de-b1f5-4a4b-a6a9-6758b1677469)/publications.rss",
          "https://pure.royalholloway.ac.uk/portal/en/persons/jinghan-zeng(b9c326b1-1329-4441-992e-3f3a3aa2ad12)/publications.rss")

dat <- data.frame(pretty_name = pretty_names,
                  base = urls)
dat <- merge(dat, data.frame(year = 2015:2020),
             all = TRUE)
dat$url <- paste0(dat$base,
                  "?publicationYearsFrom=",
                  dat$year,
                  "&publicationYearsTo=",
                  dat$year,
                  "&peerreview=true")

```

```{r loadlibs}
library(xml2)
library(rvest)
library(tidyverse)
library(purrr)
library(reshape2)
```



```{r parsepages}
## Get the description field
get_description <- function(d) {
    sel <- "(//description)[position() > 1]//text()"
    d %>%
        xml_nodes(xpath = sel) %>%
        xml_text()
}

get_title <- function(d) {
    retval <- d %>%
        read_html() %>%
        html_node(xpath = "//h2[@class = 'title']") %>%
        html_text()
}

get_properties <- function(d) {
    retval <- d %>%
        read_html() %>%
        html_node(xpath = "(//table[@class = 'properties'])") %>%
        html_table()
    return(retval)
}

if (file.exists("cache/tidied_data.rds")) {
    docs <- readRDS("cache/tidied_data.rds")
} else {
    docs <- dat %>%
        mutate(doc = map(url, read_xml)) %>%     
        mutate(doc = map(doc, get_description)) %>%
        unnest()
    
    docs <- docs %>%
        mutate(title = map_chr(doc, get_title),
               properties = map(doc, get_properties)) %>% 
        dplyr::select(pretty_name, year, title, properties) %>% 
        unnest() %>%
        dcast(pretty_name + year + title ~ X1, value.var = "X2")
    
    saveRDS(docs, file = "cache/tidied_data.rds")
}

```	


```{r formatout}

pretty_out <- function(x) {
    ## If it's a journal
    if (!is.na(x["Journal"])) {
        out <- paste0(x["title"],
                      ". *",
                      x["Journal"],
                      "*")
        if (is.na(x["Volume"])) {
            out <- paste0(out,
                          ". In production. ")
        } else {
            out <- paste0(out,
                          ", ",
                          x["Volume"])
            if (is.na(x["Issue number"])) {
                out <- paste0(out, ". ")
            } else {
                out <- paste0(out, "(",
                              x["Issue number"],
                              ")")
            }   
        }
        if (is.na(x["Pages (from-to)"])) {
            out <- paste0(out, ". ")
        } else {
            out <- paste0(out,
                          " ",
                          x["Pages (from-to)"],
                          ". ")
        }
        
         
    } else if (!is.na(x["Title of host publication"])) {
        ## It's a chapter
        out <- paste0(x["title"],
                      ". In ",
                      x["Editors"],
                      " (ed.), *",
                      x["Title of host publication"],
                      "*. ",
                      x["Publisher"],
                      ".")
    }
    return(out)
}

docs$out <- apply(docs, 1, pretty_out)

## Sanitize this
docs$out <- gsub("#", "\\#", docs$out, fixed = TRUE)
```


```{r prettyprint, eval = TRUE, results = "asis"}
docs <- subset(docs, year > 2016)
## Dump it!
for (i in pretty_names) {
    tmp <- docs %>%
        filter(pretty_name == i) %>%
        arrange(desc(year))
    tmp <- unique(tmp)
    if (nrow(tmp) > 0) {
    cat(i, " {-}\n===\n\n")
    for (j in 1:nrow(tmp)) {
        cat(" - ")
        cat(tmp$out[j])
        cat("\n\n")
    }
    }

}
```

# About this document... {-}

This document has been produced automatically using the College's
online repository, PURE ([http://pure.royalholloway.ac.uk](http://pure.royalholloway.ac.uk)). It was last updated on `r Sys.Date()`. If you
are a member of staff who has written a peer-reviewed publication which has a
publication date between 2017 and 2020 inclusive, and which is not
listed here, please update your record on PURE and ask Chris Hanretty to
recompile this document.
